### 2024-10-22 manuscript.tex
Minor fixes

Increasing climate model resolution is a common way of improving model accuracy
\citep{mauritsen2022}. This is of course limited by the available computational
power and a tradeoff with increasing parametrisation complexity. Current
computational availability and acceleration from general-purpose computing on
graphics processing units (GPGPUs) is progressing to enable km-scale (also
called k-scale) Earth system models (ESMs) and coupled atmosphsere--ocean
general circulation models (AOGCMs) in research conditions today and
operationally in the forthcoming years. Therefore, it represents a natural
advancement in climate modeling.  Global strom-resolving models (GSRMs) are
emerging as a new front in the development of high-resolution global climate
models, with horizontal grid resolutions of about 2--8 km
\citep{satoh2019,stevens2019}. This is enough to resolve mesoscale convective
storms, but smaller-scale convective plumes and smaller-scale cloud structure
remain unresolved. At a 5-km scale, non-hydrostatic processes also become
important, and for this reason such models are generally non-hydrostatic. The
terms global cloud-resolving models, or global convection-permitting/-resolving
models are also sometimes used interchangeably with GSRMs but imply that clouds
or convection are resolved explicitly, which is not entirely true for GSRMs, as
this would require an even higher horizontal resolution \citep{satoh2019}.
Representative of these efforts is the DYnamics of the Atmospheric general
circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
\citep{stevens2019,dyamond}, which is an intercomparison of nine global
storm-resolving models (GSRMs) on two 40-day time periods in summer (1 August
-- 10 September 2016) and winter (20 January - 1 March 2020). A new one-year
GSRM intercomparison is currently proposed by \cite{takasuka2024}, with the
hope of also evaluating the seasonal cycle and large-scale circulation.  An
alternative to using a computantionally costly GSRM is to train an artificial
neural network on GSRM output and use it for subgrid-scale clouds, as done with
the GSRM ICON by \cite{grundner2022}; \cite{grundner2023}.

@@

Multiple cloud properties have an effect on the shortwave (SW) and longwave
(LW) radiation. On the first order, it is the total cloud fraction, cloud
phase, and the liquid and ice water path. These are influenced by the
atmopheric thermodynamics, convection and circulation, and indirect and direct
effects of aerosols. On smaller orders, it is the cloud droplet size
distribution, ice crystal habit, cloud lifetime, and direct radiative
interaction with aerosols.  In the 6$^\mathrm{th}$ phase of the Coupled Model
Intercomparison Project [CMIP6; \citep{eyring2016}], the cloud feedback has
increased relative to CMIP5 \citep{zelinka2020}, also being one of the main
reasons for the higher climate sensitivity of CMIP6 models.

@@

SO radiation biases have been relatively large and systematic compared to the
rest of the globe since at least CMIP3 \citep{trenberth2010}, and the SO SW CRE
bias is still positive in eight analysed CMIP6 models analysed by
\cite{schuddeboom2021} over high-latitude SO, whereas over low-latitude SO it
tends to be more neutral or negative in some models. Too much absorbed SW
radiation over the SO was also identified in the GSRM SCREAM
\cite{caldwell2021}. Compensating biases are possible, such as the `too few too
bright' cloud bias, characterised by too small cloud fraction and too large
cloud albedo \citep{wall2017,kuma2020}, previously described by
\cite{webb2001}, \cite{weare2004}, \cite{zhang2005}, \cite{karlsson2008},
\cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
models. That is, a model maintains a resonable SW radiation balance by
reflecting too much SW radiation by cloudy sky but has too little cloudy sky
area overall. A study by \cite{konsta2022} showed that this type bias is still
present in six analysed CMIP6 models in tropical marine clouds, using the
GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation
(CALIPSO) Cloud Product [CALIPSO--GOCCP; \cite{chepfer2010}] and Polarization
\& Anisotropy of Reflectances for Atmospheric Sciences coupled with
Observations from a Lidar [PARASOL; \citep{lier2008}] as a reference. They
suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
Compensating cloud biases in the Australian Community Climate and Earth System
Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were
analysed by \cite{fiddes2022} and \cite{fiddes2024}.  \cite{possner2022} showed
that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
on the order of 30\% [relative to the Moderate Resolution Imaging
Spectroradiometer (MODIS)] and overestimates downwelling TOA SW radiation on
the order of 10 Wm$^\mathrm{-2}$ in  [relative to the Clouds and the Earth’s
Radiant Energy System (CERES)] in the highest model resolution run (2.5 km).
\cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
models over high-latitude SO and the total cloud fraction underestimation on
the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
analysed 48 hours of km-scale ICON limited area model NWP simulation over a
SO region adjacent to Tasmania agaist the Clouds, Aerosols, Precipitation,
Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
voyage cloud and precipitation observations. They found the ICON cloud optical
thickness underestimated relative to Himawari‐8 satellite observations, but also
large differences in cloud top phase.

@@

Altogether, we analysed about 2400 days of data from 31 voyages and one
sub-Antarctic station covering diverse longitudes and latitudes of the SO. To
achieve a like-for-like comparison with the model, we used a ground-based lidar
simulator called the Automatic Lidar and Ceilometer Framework (ALCF)
\citep{kuma2021}. We contrasted the results with the European Centre for
Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) \citep{era5} and the
Modern-Era Retrospective analysis for Research and Applications, Version 2
(MERRA-2) \citep{gelaro2017}.

>>>>

Increasing climate model resolution is a common way of improving model accuracy
\citep{mauritsen2022}. This is of course limited by the available computational
power and a tradeoff with increasing parametrisation complexity. Current
computational availability and acceleration from general-purpose computing on
graphics processing units (GPGPUs) is progressing to enable km-scale (also
called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean
general circulation models (AOGCMs) in research conditions today and
operationally in the forthcoming years. Therefore, it represents a natural
advancement in climate modeling.  Global strom-resolving models (GSRMs) are
emerging as a new front in the development of high-resolution global climate
models, with horizontal grid resolutions of about 2--8 km
\citep{satoh2019,stevens2019}. This is enough to resolve mesoscale convective
storms, but smaller-scale convective plumes and smaller-scale cloud structure
remain unresolved. At a 5-km scale, non-hydrostatic processes also become
important, and for this reason such models are generally non-hydrostatic. The
terms global cloud-resolving models, or global convection-permitting/-resolving
models are also sometimes used interchangeably with GSRMs but imply that clouds
or convection are resolved explicitly, which is not entirely true for GSRMs, as
this would require an even higher horizontal resolution \citep{satoh2019}.
Representative of these efforts is the DYnamics of the Atmospheric general
circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
\citep{stevens2019,dyamond}, which is an intercomparison of nine global
storm-resolving models (GSRMs) on two 40-day time periods in summer (1 August
-- 10 September 2016) and winter (20 January -- 1 March 2020). A new one-year
GSRM intercomparison is currently proposed by \cite{takasuka2024}, with the
hope of also evaluating the seasonal cycle and large-scale circulation.  An
alternative to using a computantionally costly GSRM is to train an artificial
neural network on GSRM output and use it for subgrid-scale clouds, as done with
the GSRM ICON by \cite{grundner2022} and \cite{grundner2023}.

@@

Multiple cloud properties have an effect on the shortwave (SW) and longwave
(LW) radiation. On the first order, it is the total cloud fraction, cloud
phase, and the liquid and ice water path. These are influenced by the
atmopheric thermodynamics, convection and circulation, and indirect and direct
effects of aerosols. On smaller orders, it is the cloud droplet size
distribution, ice crystal habit, cloud lifetime, and direct radiative
interaction with aerosols.  In the 6$^\mathrm{th}$ phase of the Coupled Model
Intercomparison Project [CMIP6; \cite{eyring2016}], the cloud feedback has
increased relative to CMIP5 \citep{zelinka2020}, also being one of the main
reasons for the higher climate sensitivity of CMIP6 models.

@@

SO radiation biases have been relatively large and systematic compared to the
rest of the globe since at least CMIP3 \citep{trenberth2010}, and the SO SW CRE
bias is still positive in eight analysed CMIP6 models analysed by
\cite{schuddeboom2021} over high-latitude SO, whereas over low-latitude SO it
tends to be more neutral or negative in some models. Too much absorbed SW
radiation over the SO was also identified in the GSRM SCREAM
\cite{caldwell2021}. Compensating biases are possible, such as the `too few too
bright' cloud bias, characterised by too small cloud fraction and too large
cloud albedo \citep{wall2017,kuma2020}, previously described by
\cite{webb2001}, \cite{weare2004}, \cite{zhang2005}, \cite{karlsson2008},
\cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
models. That is, a model maintains a resonable SW radiation balance by
reflecting too much SW radiation by cloudy sky but has too little cloudy sky
area overall. A study by \cite{konsta2022} showed that this type bias is still
present in six analysed CMIP6 models in tropical marine clouds, using the
GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation
(CALIPSO) Cloud Product [CALIPSO--GOCCP; \cite{chepfer2010}] and Polarization
\& Anisotropy of Reflectances for Atmospheric Sciences coupled with
Observations from a Lidar [PARASOL; \cite{lier2008}] as a reference. They
suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
Compensating cloud biases in the Australian Community Climate and Earth System
Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were
analysed by \cite{fiddes2022} and \cite{fiddes2024}.  \cite{possner2022} showed
that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
on the order of 30\% [relative to the Moderate Resolution Imaging
Spectroradiometer (MODIS)] and overestimates downwelling TOA SW radiation on
the order of 10 Wm$^\mathrm{-2}$ in  [relative to the Clouds and the Earth’s
Radiant Energy System (CERES)] in the highest model resolution run (2.5 km).
\cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
models over high-latitude SO and the total cloud fraction underestimation on
the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
analysed 48 hours of km-scale ICON limited area model NWP simulation over a
SO region adjacent to Tasmania agaist the Clouds, Aerosols, Precipitation,
Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
voyage cloud and precipitation observations. They found the ICON cloud optical
thickness underestimated relative to Himawari‐8 satellite observations, but also
large differences in cloud top phase.

@@

Altogether, we analysed about 2400 days of data from 31 voyages and one
sub-Antarctic station covering diverse longitudes and latitudes of the SO. To
achieve a like-for-like comparison with the model, we used a ground-based lidar
simulator called the Automatic Lidar and Ceilometer Framework [ALCF;
\cite{kuma2021}]. We contrasted the results with the European Centre for
Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 [ERA5; \cite{era5}] and the
Modern-Era Retrospective analysis for Research and Applications, Version 2
[MERRA-2; \cite{gelaro2017}].
